% !TEX root =  main.tex
\chapter{Constraints}
\label{ch: constraints}


This catalog aggregates constraints related to the management of VMs and
servers on hosting platforms. 
%
Previous chapters present key elements that may be impacted by a reconfiguration :
VM state and placement, server state, resource allocation.
%
The present chapter enumerates numerous constraints that are of a practical interest
for applications and datacenter administrators to express dependability or management
requirements such as performance, availability or security.
%
Such constraints may then be implemented in different VM managers to provide an initial
deployment or a reconfiguration process that is consistent with regards to the expressed
constraints.
 
 
Each section of this chapter details a specific constraint.
First, a definition is provided to specify the guarantees provided by the constraint.
%
A classification allows to categorize the constraint depending on the element it manipulates,
the primary concern it addresses or the typical users.
%
Several use cases illustrate then the practical interest of the constraint and examples depicts its 
impact on a reconfiguration process.
%
Finally, references to closely related constraints are provided.

Several notations are used within this chapter to write the constraints signature or sample configuration.
Chapter~\ref{ch: annexe} details these notations.


\fullVersion{
\begin{itemize}
\item Its definition to specify the guarantees the constraint provides.
%
Several use cases illustrate then the practical interest of the constraint.
%
%
Last, examples depicts the impact of the constraints on a reconfiguration process.
%
%
Several notations are used in this chapter to write constraints and configuration. Chapter~\ref{ch: annex} 
details the notations.
%
The grammar used to express the constraint signature and usage is described in Section~\ref{cstr signature}. 
%
The grammar used to express the example configurations is described in Section~\ref{sec: config signature}.

%\item Its model in terms of variables of the RPs to describe how the constraint can be formally
expressed. This model can then be used to implement the constraint on several VM manager.

%\item Its availability in VM managers. For each VM manager that provide a constraint compatible
with the specification, additional details provide explanations to the constraints. When the
constraint is available in {\btrp}, its model is discussed.

%\item A method to detect violating element. This method allows to retrieve from a configuration
the elements that may not satisfy the constraint. This provides fast heuristics to first check
if a constraint is satisfied and if not, the element that may be violating the constraint. The
detection of the violating element is however not necessarily optimal and may present some
false positive due to the combinatorial aspects of the constraint.

\item Some references to other constraints in the catalog. These references allow to navigate
among the available constraint depending on their relationships with the presented constraint. 

\end{itemize}
}
\clearpage
\input{constraints/root}
\clearpage
\input{constraints/ban}
\clearpage
\input{constraints/fence}
\clearpage
\input{constraints/quarantine}
\clearpage
\input{constraints/among}
\clearpage
\input{constraints/lonely}
\clearpage
\input{constraints/split}
\clearpage
\input{constraints/splitAmong}
\clearpage
\input{constraints/gather}
\clearpage
\input{constraints/spread}
\clearpage
\input{constraints/lazySpread}
\clearpage
\input{constraints/mostlySpread}
\clearpage
\input{constraints/preserve}
\clearpage
\input{constraints/oversubscription}
\clearpage
\input{constraints/cumulatedCapacity}
\clearpage
\input{constraints/singleCapacity}
\clearpage
\input{constraints/minSpareResources}
\clearpage
\input{constraints/maxSpareResources}
\clearpage
\input{constraints/maxOnlines}
\clearpage
\input{constraints/offline}
\clearpage
\input{constraints/online}
\clearpage

%\input{constraints/borderPatrol}
%\clearpage
%\input{constraints/globalOverSubscription}
%\clearpage
%\input{constraints/globalSpareCapacity}
%\clearpage
%\input{constraints/platform}
%\clearpage
%\input{constraints/reconfigurable}
%\clearpage
%\input{constraints/running}
%\clearpage
%\input{constraints/singleSpareCapacity}
%\clearpage
%\input{constraints/sleeping}
%\clearpage
%\input{constraints/terminating}
%\clearpage
%\input{constraints/waiting}