\documentclass[a4paper]{report}
\usepackage{RR}
\usepackage[shortVersion]{btrpcc}
\usepackage[T1]{fontenc}
\makeindex

\setcounter{tocdepth}{1}

%%%
\RRdate{08/19/2012}
\RRauthor{
Fabien Hermenier\thanks[oasis]{INRIA - CNRS - I3S, Univ. Nice Sophia-Antipolis, --fabien.hermenier@inria.fr}}


\RRequipe{OASIS}
\RCSophia
\RRetitle{The BtrPlace Constraints Catalog}
\RRtitle{The BtrPlace Constraints Catalog}




\RRabstract{
Datacenters provide through virtualization, platforms of choice to host a large range
of applications. At submission, each tenant provides through a Service Level Agreement
its concerns in terms of VMs management. These concerns are typically related
to performance, reliability, or isolation criteria. In parallel, platform administrators have
management criteria related to power management,  resource allocation or security
concerns.

All of these constraints have to be considered by the VM manager running on the hosting
platform to make management decisions aligned with the tenants and the administrators
expectations.  
%
Each existing VM manager provides its own constraints to address some of
these criteria or allow to integrate external constraints. However, the semantic of a constraint
varies with the VM manager while constraints' users lack of expertise when they have to
select or develop new constraints matching their expectations.

This catalog gathers constraints that are of a practical interest to manage VMs
and servers in a hosting platform such as a datacenter or a cloud. Each constraint
is associated with practical use cases and classification criteria to help users at
understanding its interest. In addition, a formal definition and a vendor neutral model
allow to understand the constraint impact on a VM manager decision.
Finally, the availability of each constraint in common VM manager is described 
while its formal model provides the fundaments for an implementation
in flexible VM managers.
}

\RRmotcle{Virtualisation; Centre de donn\'ees; Gestion des ressources; Qualit\'e de service; Reconfiguration}

\RRkeyword{Virtualization; Datacenter; Resource Management; Service Level Agreements; Reconfiguration}

\RCSophia

\begin{document}
\makeRT
\tableofcontents 
 \clearpage
%\listoffigures
%\listoftables
%\lstlistoflistings
\input{intro}
%\input{hostingPlatform}
\input{reconfiguration}
\fullVersion{
\input{model}
}
\input{constraints.tex}


\input{annexe}

\input{inheritance}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\indexname}
\printindex

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{References}
\bibliographystyle{abbrv}
\bibliography{references}


\end{document}